\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\ifdefined\pdfgentounicode
 \input{glyphtounicode}
\fi

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
 \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

\ifdefined\pdfgentounicode
 \pdfgentounicode=1
\fi

\newcommand{\resumeItem}[1]{
 \item\small{{#1 \vspace{-1.5pt}}}
}

\newcommand{\resumeSubheading}[4]{
 \vspace{-1pt}\item
 \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
 \textbf{#1} & #2 \\
 \textit{\small#3} & \textit{\small #4} \\
 \end{tabular*}\vspace{-6pt}
}

\newcommand{\resumeProjectHeadingURL}[3]{
 \item
 \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
 \small#1 & #2 \\
 \end{tabular*}\vspace{-3pt}\\
 \hspace{0.05in}{\small\href{#3}{\underline{#3}}}\vspace{-2pt}
}

\newcommand{\resumeProjectHeadingLink}[4]{
 \item
 \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
 \small#1 & #2 \\
 \end{tabular*}\vspace{-3pt}\\
 \hspace{0.05in}{\small\href{#4}{\underline{#3}}}\vspace{-2pt}
}

\newcommand{\resumeProjectHeading}[2]{
 \item
 \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
 \small#1 & #2 \\
 \end{tabular*}\vspace{-6pt}
}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[topsep=0pt, partopsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-4pt}}

\begin{document}

\begin{center}
 \textbf{\Huge \scshape Dawoud Mahmud} \\ \vspace{1pt}
 \small 510-505-4624 $|$ \href{mailto:dawoud.mahmud@gmail.com}{\underline{dawoud.mahmud@gmail.com}} $|$
 \href{https://linkedin.com/in/dawoud-mahmud}{\underline{www.linkedin.com/in/dawoud-mahmud/}} $|$
 \href{https://github.com/DawoudMahmud}{\underline{github.com/DawoudMahmud}}
\end{center}

\section{Summary}
 \begin{itemize}[leftmargin=0.15in, label={}]
 \small{\item{
Customer-facing full-stack engineer with CS/ML training, software QA experience, AI workflow tooling, and hands-on product development. Strong fit for forward-deployed engineering: translating ambiguous customer workflows into technical plans, building data-backed features and integrations, documenting launches, debugging live issues, and communicating clearly with both users and engineers.
 }}
 \end{itemize}

\section{Education}
 \resumeSubHeadingListStart
 \resumeSubheading
 {Georgia Institute of Technology}{Atlanta, GA}
 {M.S. in Computer Science, Machine Learning (GPA: 3.83)}{Aug. 2024 -- Present}
 \resumeSubheading
 {University of California, Irvine}{Irvine, CA}
 {B.S. in Computer Science, Minor in Mathematics}{Graduated 2022}
 \resumeSubHeadingListEnd

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
 \small{\item{
 \textbf{Languages}{: Python, Go, Java, JavaScript, TypeScript, Swift, C, C++, SQL, Bash} \\
 \textbf{Full-Stack}{: React, Next.js, Node.js, REST APIs, Spring Boot, Convex, Clerk, Stripe, Postman} \\
 \textbf{Cloud/Data}{: AWS Certified Cloud Practitioner, Docker, Terraform, CI/CD, Vercel, MySQL, DynamoDB, Pandas, NumPy} \\
 \textbf{AI/Automation}{: Claude Code, Codex, OpenClaw, Claude Opus, LLM APIs, Prompt/Context Design, Workflow Automation} \\
 \textbf{Practices}{: Technical Troubleshooting, Customer Communication, QA, Documentation, Git, Linux/Unix, Agile/Scrum}
 }}
 \end{itemize}

\section{Experience}
 \resumeSubHeadingListStart

 \resumeSubheading
 {Specialist}{Aug. 2024 -- Present}
 {Apple, Inc.}{Santa Clara, CA}
 \resumeItemListStart
 \resumeItem{Resolved technical issues for 20+ customers daily across hardware, software, account, device, and workflow problems; translated ambiguous root causes into clear, customer-safe next steps.}
 \resumeItem{Drove \$84K+ in revenue by discovering business needs, recommending technical solutions, and onboarding 72+ small business clients through product selection, setup guidance, and adoption support.}
 \resumeItemListEnd

 \resumeSubheading
 {Software QA Engineer Intern}{May 2021 -- Sep. 2021}
 {Extron Inc.}{Milpitas, CA}
 \resumeItemListStart
 \resumeItem{Drove a 75\% migration of a legacy shipping platform by documenting target architecture, validating workflows, and defining the next-phase technical roadmap.}
 \resumeItem{Executed 80+ user journey tests per sprint to validate business logic, reproduce defects, document edge cases, and improve release reliability across shipping workflows.}
 \resumeItemListEnd

 \resumeSubHeadingListEnd

\section{Projects}
 \resumeSubHeadingListStart

 \resumeProjectHeadingLink
 {\textbf{Mehndi Market} $|$ \emph{Next.js, TypeScript, Convex, Clerk, Vercel, Stripe} $|$ \emph{In Progress}}{}
 {Preview deployment}
 {https://mehndimarket-i67kxg1pm-mehndimarket.vercel.app?x-vercel-protection-bypass=QPPVMEod33V13dhxj9e0nnhBwCoepEdI\&x-vercel-set-bypass-cookie=true}
 \resumeItemListStart
 \resumeItem{Building an early-stage full-stack marketplace with authenticated user flows, seller onboarding, listing discovery, and a curated storefront.}
 \resumeItem{Implemented Convex schema, queries, mutations, validation, active-listing indexes, seller metadata, price fields, and location support for data-backed marketplace workflows.}
 \resumeItem{Own roadmap across seller setup, buyer discovery, payments, and trust workflows, translating messy marketplace requirements into implementation-ready product specs.}
 \resumeItemListEnd

 \resumeProjectHeadingURL
 {\textbf{Terraform Provider Mikrotik} $|$ \emph{Go, Terraform, RouterOS, Infrastructure-as-Code}}{}
 {https://github.com/ddelnano/terraform-provider-mikrotik/pull/176}
 \resumeItemListStart
 \resumeItem{Implemented Terraform resource logic for WireGuard VPN interfaces and peers in Go, including provider schemas, CRUD operations, RouterOS command mappings, and invalid-resource error handling.}
 \resumeItem{Collaborated with open-source maintainers on test coverage, acceptance criteria, review feedback, and release readiness for production infrastructure automation.}
 \resumeItemListEnd

 \resumeProjectHeading
 {\textbf{AI Workflow Automation} $|$ \emph{Claude Code, Codex, OpenClaw, Python, Shell}}{}
 \resumeItemListStart
 \resumeItem{Built repeatable AI-assisted workflows for research, document generation, implementation planning, debugging, QA, and file-system automation.}
 \resumeItem{Designed reusable prompts, task instructions, output checks, and human review loops to keep long-running AI workflows reliable across ambiguous tasks.}
 \resumeItemListEnd

 \resumeSubHeadingListEnd

\end{document}